A decomposition Approach for solving the JSP using multi-shot ASP\thanks{Supported by organization x.}

### 2022-01-11 ICLP Paper/samplepaper3.tex
First draft of ICLP Paper

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{helvet,times,courier}
\usepackage{listings}
\usepackage[inline]{enumitem}
\lstset{numberbychapter=false,numbers=left,numberblanklines=false,basicstyle=\footnotesize\ttfamily,xleftmargin=5ex}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{A decomposition Approach for solving the JSP using multi-shot ASP\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Mohammed M. S. El-Kholany\inst{1}\orcidID{0000-0002-1088-2081} \and
Martin Gebser\inst{1,2}\orcidID{0000-0002-8010-4752} \and
Konstantin Schekotihin\inst{1}\orcidID{0000-0002-0286-0958}}
%
\authorrunning{M. El-Kholany et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Alpen-Adria-Universität Klagenfurt, Klagenfurt, Austria 
\email{\{mohammed.el-kholany, martin.gebser and konstantin.schekotihin\}@aau.at}\\
%\url{http://www.springer.com/gp/computer-science/lncs} \and
Technische Universität Graz, Graz, Austria\\
\email{mgebser@ist.tugraz.at}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{Job-shop Scheduling Problem  \and Answer Set Programming \and Decomposition.}
\end{abstract}
%
%
%
\section{Introduction}
In today's competitive markets, manufacturers have to respond quickly to orders and meet shipping dates committed to the customers. This requires the ability to schedule production activities to use the available scarce resources efficiently. Effective scheduling techniques are essential in complex manufacturing systems such as semiconductor manufacturing. In general, scheduling operations is one of the most critical issues in the planning and managing of the manufacturing processes\cite{uzsoy2000performance}.

@@

In order to encode the problem using ASP, we should define a set of predicates that represents the problem instances. For instance, the operations are encoded with the predicate \lstinline{operation/2} where the first variable denotes the job number and the second is the operation number, see lines \ref{prg:facts:ops:begin}-\ref{prg:facts:ops:end} in Listing \ref{prg:facts}. The time needed to finish an operation is represented by the predicate \lstinline{pro/3} in which the operation is determined by the first two terms and the third represents the processing time in lines \ref{prg:facts:pro:begin}-\ref{prg:facts:pro:end}. For the machine assignment, the predicate \lstinline{assign/3} shows that a particular operation is executed by a machine in lines \ref{prg:facts:mach:begin}-\ref{prg:facts:mach:end} For instance, \emph{operation(1,1)} is processed by machine 2. 
\lstinputlisting[float=bt,mathescape=true,escapeinside={\#(}{\#)},basicstyle={\ttfamily\small},label=prg:facts,caption={Problem instance}, linerange={1-11} ]{listing/facts.lp}

@@

We prioritize the operations based on the estimated starting time, calculating an index for each operation. The operation with a shorter estimated start time will get a smaller index than the others with a higher estimated starting time. If the estimated starting time between two operations or more is similar, we check the processing time; the higher the processing time, the smaller index, and, therefore, the higher priority to be assigned earlier. If the processing time is equal, we look at the operation number and then the job number. This strategy is encoded in lines \ref{prg:assignment_process:rank:begin}-\ref{prg:assignment_process:rank:end}. The fourth rule in lines \ref{prg:assignment_process:assign:begin}-\ref{prg:assignment_process:assign:end} is to assign each operation to a time winodw.

@@

\lstinputlisting[float=bt,mathescape=true,escapeinside={\#(}{\#)},basicstyle={\ttfamily\small},label=prg:base,caption={base-prog}, linerange={1-12} ]{listing/base.lp}

@@

\lstinputlisting[float=bt,mathescape=true,escapeinside={\#(}{\#)},basicstyle={\ttfamily\small},label=prg:sub,caption={sub-prog}, linerange={1-40} ]{listing/sub_pro.lp}

The third part of the scheduler is shown in Listing \ref{prg:diff} that handles the difference constraints between the operations. The first rule in lines \ref{prg:diff_log:non_nega:begin}-\ref{prg:diff_log:non_nega:end} ensures that all the operations will be processed starting from time $0$. The second and the third rule fix the execution time of the operations scheduled in the previous TW. The fourth rule aimed to avoid overlapping the operations that either belongs to the same job or are assigned to the same machine. The fifth rule ensures that the ending time of all operations will not exceed the bound variable, which is the makespan in our case. 
\lstinputlisting[float=bt,mathescape=true,escapeinside={\#(}{\#)},basicstyle={\ttfamily\small},label=prg:diff,caption={diff-log}, linerange={1-20} ]{listing/diff_log.lp}

\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation, etc., do not need, either.

Subsequent paragraphs, however, are indented.

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\bibliographystyle{splncs04}
\bibliography{Ref}

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{helvet,times,courier}
\usepackage{listings}
\usepackage[inline]{enumitem}
\usepackage{adjustbox}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\lstset{numberbychapter=false,numbers=left,numberblanklines=false,basicstyle=\footnotesize\ttfamily,xleftmargin=5ex,breaklines=false}
\usepackage{multirow}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{A decomposition Approach for solving the JSP using multi-shot ASP\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Mohammed M. S. El-Kholany\inst{1}\orcidID{0000-0002-1088-2081} \and
Martin Gebser\inst{1,2}\orcidID{0000-0002-8010-4752} \and
Konstantin Schekotihin\inst{1}\orcidID{0000-0002-0286-0958}}
%
\authorrunning{M. El-Kholany et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Alpen-Adria-Universität Klagenfurt, Klagenfurt, Austria 
\email{\{mohammed.el-kholany, martin.gebser and konstantin.schekotihin\}@aau.at}\\
%\url{http://www.springer.com/gp/computer-science/lncs} \and
Technische Universität Graz, Graz, Austria\\
\email{mgebser@ist.tugraz.at}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
    Scheduling plays a significant role in the success of any manufacturing system where the tasks are assigned to a limited number of resources to be scheduled. Job-shop Scheduling Problem (JSP) is one of the most challenging problems in production systems. JSP deals with assigning the tasks to a set of machines and determining the sequence of the tasks on each machine while completing them as early as possible. This paper applied a decomposition approach that splits the problem into a pre-defined set of small problems called Time Windows (TWs) and solves each separately in sequential order. Our proposed model is split into two main phases for solving the (JSP). The decomposition phase assigns each operation to a particular TW while satisfying the precedence constraint. The second phase is the scheduling phase, in which the model starts to optimize the first TW and continues until finishing the last TW. We built our model using Answer Set Programming (ASP). A Multi-shot solving paradigm is used to deal with the decomposition approach and differenc logic to handle the constraints. To evaluate the proposed work, we tested our model on a set of benchmark instances with different sizes and the results showed that the multi-shot solving is better than the single-shot when the number of operations increases. 
\keywords{Job-shop Scheduling Problem  \and Answer Set Programming \and Decomposition.}
\end{abstract}
%
%
%
\section{Introduction}
In today's competitive markets, manufacturers have to respond quickly to orders and meet shipping dates committed to the customers. This requires the ability to schedule production activities to use the available scarce resources efficiently. Effective scheduling techniques are essential in complex manufacturing systems such as semiconductor manufacturing. In general, scheduling operations is one of the most critical issues in the planning and managing of the manufacturing processes\cite{uzsoy2000performance}.

@@

In order to encode the problem using ASP, we should define a set of predicates that represents the problem instances. For instance, the operations are encoded with the predicate \lstinline{operation/2} where the first variable denotes the job number and the second is the operation number, see lines \ref{prg:facts:ops:begin}-\ref{prg:facts:ops:end} in Listing \ref{prg:facts}. The time needed to finish an operation is represented by the predicate \lstinline{pro/3} in which the operation is determined by the first two terms and the third represents the processing time in lines \ref{prg:facts:pro:begin}-\ref{prg:facts:pro:end}. For the machine assignment, the predicate \lstinline{assign/3} shows that a particular operation is executed by a machine in lines \ref{prg:facts:mach:begin}-\ref{prg:facts:mach:end}. For instance, \emph{operation(1,1)} is processed by machine 2. 
\lstinputlisting[float=bt,mathescape=true,escapeinside={\#(}{\#)},basicstyle={\ttfamily\small},label=prg:facts,caption={Problem instance}, linerange={1-11} ]{listing/facts.lp}

@@

We prioritize the operations based on the estimated starting time, calculating an index for each operation. The operation with a shorter estimated start time will get a smaller index than the others with a higher estimated starting time. If the estimated starting time between two operations or more is similar, we check the processing time; the higher the processing time, the smaller index, and, therefore, the higher priority to be assigned earlier. If the processing time is equal, we look at the operation number and then the job number. This strategy is encoded in lines \ref{prg:assignment_process:rank:begin}-\ref{prg:assignment_process:rank:end}. The fourth rule in lines \ref{prg:assignment_process:assign:begin}-\ref{prg:assignment_process:assign:end} is to assign each operation to a time window.

@@

\lstinputlisting[float=bt,mathescape=true,escapeinside={\#(}{\#)},basicstyle={\ttfamily\small},label=prg:base,caption={base-prog} ]{listing/base.lp}

@@

% \lstinputlisting[float=bt,mathescape=true,escapeinside={\#(}{\#)},basicstyle={\ttfamily\small},label=prg:sub,caption={sub-prog}, linerange={1-40} ]{listing/sub_pro.lp}

The third part of the scheduler is shown in Listing \ref{prg:diff} that handles the difference constraints between the operations. The first rule in lines \ref{prg:diff_log:non_nega:begin}-\ref{prg:diff_log:non_nega:end} ensures that all the operations will be processed starting from time $0$. The second and the third rule fix the execution time of the operations scheduled in the previous TW. The fourth rule aimed to avoid overlapping the operations that either belongs to the same job or are assigned to the same machine. The fifth rule ensures that the ending time of all operations will not exceed the bound variable, which is the makespan in our case. 
\lstinputlisting[float=bt,mathescape=true,escapeinside={\#(}{\#)},basicstyle={\ttfamily\small},label=prg:diff,caption={diff-log}]{listing/diff_log.lp}

\section{Results}
This section will show the computational experiments that we conducted to test the performance of our proposed model. In order to evaluate our model, we performed several experiments on a set of benchmark instances with a different number of jobs and machines. The benchmark instances we considered are generated in 1993 by E. Taillard \cite{taillard1993benchmarks}, and the size of the problems variate starting from $6$ jobs and $6$ machines till $100$ jobs and $20$ machines. We have decided to focus on $3$ different sizes of the problem, which are $50$ jobs, $15$ machines, $50$ jobs and $20$ machines and $100$ jobs and $20$ machines. Our experiments had been conducted on a laptop with Intel(R) Core(TM) i7-8650U CPU @ 1.90GHz 2.11 GHz, 8th generation, and $16$ GB. We split the problem into a different number of TWs starting from $2$ - $10$ throughout each size of the instances we focused on to investigate the most appropriate number of TWs. We run the model with a fixed amount of time $1000$ seconds. We set this amount because we observed that increasing the time more did not provide better results, and when we reduced it, the results became worse. The next table shows the obtained results with solving $50 \times 15$.

\begin{table}[ht]
	\fontsize{19pt}{30pt}
	\caption{Results for JSP $50 \times 15$ instances with different TWs} \label{tab: Table01}
	\centering
	%\resizebox{\columnwidth}{!}{%
	\rotatebox{90}{
	\begin{adjustbox}{width=1.7\textwidth}
	\begin{tabular}{|M{2.0cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|}

	%\begin{tabular}{l c c c | c c c | c c c | c c c | c c c | c c c | c c c | c c c | c c c | c c c}
		\hline
		\multirow{3}*{\textbf{{\large Instances}}}  &  \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 01}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 02}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 03}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 04}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 05}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 10}}}} \\[1cm]

		\hline
		& {\large Makespan} & {\Large Timeout}  & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} &  {\large Makespan} & {\Large Timeout} & {\large Interr-calls}\\[1cm]

		{\LARGE TA51} & $3594.0$ & $1000.0$ & $1.0$ & $\mathbf{3442.0}$ & $1000.0$ & $2.0$ & $3843.0$ & $1000.0$ & $3.0$ & $4049.0$ & $1000.0$ & $4.0$ & $3965.0$ & $994.5$ & $4.0$ & $4269.0$ & $287.7$ & $2.0$\\[1cm]

		{\LARGE TA52} & $3638.0$ & $1000.0$ & $1.0$ & $3750.0$ & $1000.0$ & $2.0$ & $\mathbf{3613.0}$ & $1000.0$ & $3.0$ & $3850.0$ & $1000.0$ & $4.0$ & $4022.0$ & $1000.0$ & $5.0$ & $4256.0$ & $241.1$ & $1.0$\\[1cm]

		{\LARGE TA53} & $\mathbf{3388.0}$ & $1000.0$ & $1.0$ & $3497.0$ & $1000.0$ & $2.0$ & $3566.0$ & $1000.0$ & $3.0$ & $3618.0$ & $1000.0$ & $4.0$ & $3803.0$ & $1000.0$ & $5.0$ & $4065.0$ & $206.6$ & $2.0$\\[1cm]

		{\LARGE TA54} & $3434.0$ & $1000.0$ & $1.0$ & $3489.0$ & $1000.0$ & $2.0$ & $\mathbf{3433.0}$ & $1000.0$ & $3.0$ & $3766.0$ & $1000.0$ & $4.0$ & $3732.0$ & $1000.0$ & $5.0$ & $4079.0$ & $241.5$ & $2.0$\\[1cm]

		{\LARGE TA55} & $3599.0$ & $1000.0$ & $1.0$ & $\mathbf{3439.0}$  & $1000.0$ & $2.0$ & $3745.0$ & $1000.0$ & $3.0$ & $3878.0$ & $1000.0$ & $4.0$ & $4046.0$ & $1000.0$ & $5.0$ & $4336.0$ & $424.2$ & $4.0$\\	[1cm]

		{\LARGE TA56} & $\mathbf{3465.0}$ & $1000.0$ & $1.0$ & $3471.0$ & $1000.0$ & $2.0$ & $3583.0$ & $1000.0$ & $3.0$ & $4117.0$ & $1000.0$ & $4.0$ & $4069.0$ & $1000.0$ & $5.0$ & $4147.0$ & $212.0$ & $2.0$\\[1cm]

		{\LARGE TA57} & $3695.0$ & $1000.0$ & $1.0$ & $3779.0$ & $1000.0$ & $2.0$ & $\mathbf{3665.0}$ & $1000.0$ & $3.0$ & $4199.0$ & $1000.0$ & $4.0$ & $4096.0$ & $1000.0$ & $5.0$ & $3960.0$ & $208.8$ & $2.0$\\[1cm]

		{\LARGE TA58} & $\mathbf{3642.0}$ & $1000.0$ & $1.0$ & $3777.0$ & $1000.0$ & $2.0$ & $3787.0$ & $1000.0$ & $3.0$ & $3765.0$ & $1000.0$ & $4.0$ & $3826.0$ & $810.3$ & $4.0$ & $4109.0$ & $137.9$ & $1.0$\\[1cm]

		{\LARGE TA59} & $3497.0$ & $1000.0$ & $1.0$ & $\mathbf{3385.0}$ & $1000.0$ & $2.0$ & $3642.0$ & $1000.0$ & $3.0$ & $4032.0$ & $1000.0$ & $4.0$ & $3909.0$ & $1000.0$ & $5.0$ & $4227.0$ & $404.1$ & $3.0$\\[1cm]

		{\LARGE TA60} & $3469.0$ & $1000.0$ & $1.0$ & $\mathbf{3219.0}$ & $1000.0$ & $2.0$ & $3338.0$ & $1000.0$ & $3.0$ & $3426.0$ & $1000.0$ & $4.0$ & $3622.0$ & $1000.0$ & $5.0$ & $3825.0$ & $32.7$ & $0.0$\\ [1cm]
        \hline

		\multirow{3}{*}{{\large AVG}} & \multirow{3}{*}{$3542.1$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$1.0$} & \multirow{3}{*}{$\mathbf{3524.8}$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$2.0$} & \multirow{3}{*}{$3621.5$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$3.0$} & \multirow{3}{*}{$3870.0$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$4.0$} & \multirow{3}{*}{$3908.1$} & \multirow{3}{*}{$978.7$} & \multirow{3}{*}{$4.8$} &  \multirow{3}{*}{$4127.3$} & \multirow{3}{*}{$239.7$} & \multirow{3}{*}{$1.9$}\\ [1cm]

		\hline

	\end{tabular}
    \end{adjustbox}
	}

\end{table}

\begin{table}[ht]
	\fontsize{19pt}{30pt}
	\caption{Results for JSP $50 \times 20$ instances with different TWs} \label{tab: Table02}
	\centering
	%\resizebox{\columnwidth}{!}{%
	\rotatebox{90}{
	\begin{adjustbox}{width=1.7\textwidth}
    \begin{tabular}{|M{2.0cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|}

	%\begin{tabular}{l c c c | c c c | c c c | c c c | c c c | c c c | c c c | c c c | c c c | c c c}
		\hline
		\multirow{3}*{\textbf{{\large Instances}}}  &  \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 01}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 02}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 03}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 04}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 05}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 10}}}} \\[1cm]

		\hline
		& {\large Makespan} & {\Large Timeout}  & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} &  {\large Makespan} & {\Large Timeout} & {\large Interr-calls}\\[1cm]

		{\LARGE TA61} & $3919.0$ & $1000.0$ & $1.0$ & $\mathbf{3537.0}$ & $1000.0$ & $2.0$ & $3604.0$ & $1000.0$ & $3.0$ & $4231.0$ & $1000.0$ & $4.0$ & $4051.0$ & $1000.0$ & $5.0$ & $4463.0$ & $253.0$ & $2.0$\\[1cm]

		{\LARGE TA62} & $3982.0$ & $1000.0$ & $1.0$ & $3610.0$ & $1000.0$ & $2.0$ & $\mathbf{3602.0}$ & $1000.0$ & $3.0$ & $3848.0$ & $1000.0$ & $4.0$ & $3955.0$ & $925.4$ & $4.0$  & $4445.0$ & $326.9$ & $3.0$\\[1cm]

		{\LARGE TA63} & $3746.0$ & $1000.0$ & $1.0$ & $\mathbf{3285.0}$ & $1000.0$ & $2.0$ & $3410.0$ & $1000.0$ & $3.0$ & $3654.0$ & $1000.0$ & $4.0$ & $4295.0$ & $1000.0$ & $5.0$ & $4717.0$ & $311.3$ & $3.0$\\[1cm]

		{\LARGE TA64} & $3610.0$ & $1000.0$ & $1.0$ & $\mathbf{3362.0}$ & $1000.0$ & $2.0$ & $3463.0$ & $1000.0$ & $3.0$ & $3670.0$ & $1000.0$ & $4.0$ & $3929.0$ & $821.3$ & $4.0$ & $4111.0$ & $357.4$ & $2.0$\\[1cm]

		{\LARGE TA65} & $3781.0$ & $1000.0$ & $1.0$ & $\mathbf{3434.0}$ & $1000.0$ & $2.0$ & $3550.0$ & $1000.0$ & $3.0$ & $3639.0$ & $1000.0$ & $4.0$ & $3805.0$ & $1000.0$ & $5.0$ & $4406.0$ & $81.6$ & $0.0$\\	[1cm]

		{\LARGE TA66} & $3895.0$ & $1000.0$ & $1.0$ & $3582.0$ & $1000.0$ & $2.0$ & $\mathbf{3504.0}$ & $1000.0$ & $3.0$ & $4082.0$ & $1000.0$ & $4.0$ & $4077.0$ & $1000.0$ & $5.0$ & $4210.0$ & $249.2$ & $2.0$\\[1cm]

		{\LARGE TA67} & $3866.0$ & $1000.0$ & $1.0$ & $\mathbf{3547.0}$ & $1000.0$ & $2.0$ & $3571.0$ & $1000.0$ & $3.0$ & $4041.0$ & $1000.0$ & $4.0$ & $4115.0$ & $1000.0$ & $5.0$ & $4387.0$ & $285.5$ & $2.0$\\[1cm]

		{\LARGE TA68} & $3763.0$ & $1000.0$ & $1.0$ & $\mathbf{3476.0}$ & $1000.0$ & $2.0$ & $3759.0$ & $1000.0$ & $3.0$ & $3897.0$ & $1000.0$ & $4.0$ & $3855.0$ & $1000.3$ & $5.0$ & $4063.0$ & $210.6$ & $2.0$\\[1cm]

		{\LARGE TA69} & $4121.0$ & $1000.0$ & $1.0$ & $\mathbf{3748.0}$ & $1000.0$ & $2.0$ & $3803.0$ & $1000.0$ & $3.0$ & $4116.0$ & $1000.0$ & $4.0$ & $3937.0$ & $1000.0$ & $5.0$ & $4518.0$ & $111.0$ & $1.0$\\[1cm]

		{\LARGE TA70} & $4111.0$ & $1000.0$ & $1.0$ & $3827.0$ & $1000.0$ & $2.0$ & $\mathbf{3791.0}$ & $1000.0$ & $3.0$ & $4008.0$ & $1000.0$ & $4.0$ & $4044.0$ & $1000.0$ & $5.0$ & $4651.0$ & $365.2$ & $3.0$\\ [1cm]
        \hline

		\multirow{3}{*}{{\LARGE AVG}} & \multirow{3}{*}{$3879.4$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$1.0$} & \multirow{3}{*}{$\mathbf{3540.8}$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$2.0$} & \multirow{3}{*}{$3605.7$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$3.0$} & \multirow{3}{*}{$3918.6$} & \multirow{3}{*}{$1000.0$} & \multirow{3}{*}{$4.0$} & \multirow{3}{*}{$4006.3$} & \multirow{3}{*}{$974.3$} & \multirow{3}{*}{$4.8$} & \multirow{3}{*}{$4397.1$} & \multirow{3}{*}{$245.2$} & \multirow{3}{*}{$2.0$}\\ [1cm]

		\hline

	\end{tabular}
    \end{adjustbox}
	}

\end{table}

\begin{table}[ht]
	\fontsize{19pt}{30pt}
	\caption{Results for JSP $100 \times 20$ instances with different TWs} \label{tab: Table03}
	\centering
	%\resizebox{\columnwidth}{!}{%
	\rotatebox{90}{
	\begin{adjustbox}{width=1.7\textwidth}
		%\begin{tabular}[m]{|m{2cm}|*{17}{c}|c|}
    \begin{tabular}{|M{2.0cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|M{1.9cm}|M{1.9cm}|M{1.2cm}|}

        %\begin{tabular}{l c c c | c c c | c c c | c c c | c c c | c c c | c c c | c c c | c c c | c c c}
        \hline
        \multirow{3}*{\textbf{{\large Instances}}}  &  \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 01}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 02}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 03}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 04}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 05}}}} & \multicolumn{3}{|c|}{\multirow{3}{*}{\textbf{{\LARGE TW 10}}}} \\[1cm]

        \hline
        & {\large Makespan} & {\Large Timeout}  & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} & {\large Makespan} & {\Large Timeout} & {\large Interr-calls} &  {\large Makespan} & {\Large Timeout} & {\large Interr-calls}\\[1cm]

		{\LARGE TA71} & $52147.0$ & $1000.0$ & $1.0$ & $21345.0$ & $1000.0$ & $2.0$ & $7641.0$ & $1000.0$ & $3.0$ & $7471.0$ & $1000.0$ & $4.0$ & $\mathbf{7226.0}$ & $1000.0$ & $5.0$ & $8478.0$ & $1000.0$ & $10.0$\\[1cm]

		{\LARGE TA72} & $45196.0$ & $1000.0$ & $1.0$ & $23505.0$ & $1000.0$ & $2.0$ & $\mathbf{6750.0}$ & $1000.0$ & $3.0$ & $7134.0$ & $1000.0$ & $4.0$ & $7300.0$ & $1000.0$ & $5.0$ & $8164.0$ & $1000.0$ & $10.0$\\[1cm]

		{\LARGE TA73} & $36548.0$ & $1000.0$ & $1.0$ & $24995.0$ & $1000.0$ & $2.0$ & $7121.0$ & $1000.0$ & $3.0$ & $\mathbf{7027.0}$ & $1000.0$ & $4.0$ & $7416.0$ & $1000.0$ & $5.0$ & $7975.0$ & $1000.0$ & $10.0$\\[1cm]

		{\LARGE TA74} & $52973.0$ & $1000.0$ & $1.0$ & $25230.0$ & $1000.0$ & $2.0$ & $6703.0$ & $1000.0$ & $3.0$ & $\mathbf{6634.0}$ & $1000.0$ & $4.0$ & $7062.0$ & $1000.0$ & $4.0$ & $7994.0$ & $1000.0$ & $10.0$\\[1cm]

		{\LARGE TA75} & $45316.0$ & $1000.0$ & $1.0$ & $23651.0$  & $1000.0$ & $2.0$ & $\mathbf{7042.0}$ & $1000.0$ & $3.0$ & $7511.0$ & $1000.0$ & $4.0$ & $7070.0$ & $1000.0$ & $5.0$ & $7934.0$ & $1000.0$ & $10.0$\\[1cm]

		{\LARGE TA76} & $53532.0$ & $1000.0$ & $1.0$ & $40944.0$ & $1000.0$ & $2.0$ & $7067.0$ & $1000.0$ & $3.0$ & $\mathbf{6879.0}$ & $1000.0$ & $4.0$ & $7061.0$ & $1000.0$ & $5.0$ & $7938.0$ & $1000.0$ & $10.0$\\[1cm]

		{\LARGE TA77} & $45003.0$ & $1000.0$ & $1.0$ & $24517.0$ & $1000.0$ & $2.0$ & $6947.0$ & $1000.0$ & $3.0$ & $\mathbf{6929.0}$ & $1000.0$ & $4.0$ & $7307.0$ & $1000.0$ & $5.0$ & $7773.0$ & $1000.0$ & $10.0$\\[1cm]

		{\LARGE TA78} & $41380.0$ & $1000.0$ & $1.0$ & $24686.0$ & $1000.0$ & $2.0$ & $6917.0$ & $1000.0$ & $3.0$ & $\mathbf{6793.0}$ & $1000.0$ & $4.0$ & $7215.0$ & $1000.0$ & $5.0$ & $7986.0$ & $1000.0$ & $10.0$\\[1cm]

		{\LARGE TA79} & $48827.0$ & $1000.0$ & $1.0$ & $24401.0$ & $1000.0$ & $2.0$ & $6913.0$ & $1000.0$ & $3.0$ & $\mathbf{6621.0}$ & $1000.0$ & $4.0$ & $6645.0$ & $1000.0$ & $5.0$ & $7405.0$ & $1000.0$ & $10.0$\\[1cm]

		{\LARGE TA80} & $46939.0$ & $1000.0$ & $1.0$ & $22833.0$ & $1000.0$ & $2.0$ & $6925.0$ & $1000.0$ & $3.0$ & $\mathbf{6645.0}$ & $1000.0$ & $4.0$ & $6647.0$ & $1000.0$ & $5.0$ & $7609.0$ & $1000.0$ & $10.0$\\ [1cm]
        \hline
